Dismal Code: Studying the Evolution of Security Vulnerabilities

### 2013-02-06 docs/msr.tex
bib entries for the size/bugs issue

The motivation behind our work is to validate if programmers tend to care for
such high-risk bugs when they release a new version of their software. In
addition, we want to investigate other critical aspects associated with such
vulnerabilities. For instance, we want to elaborate more on the relation of security
bugs not only with performance bugs (as Zaman et al.~\cite{ZAH11} have already
did) but also with other bug categories. In the same manner, we want to check
if the relation between an artifact's size and its' software bugs applies 
to security bugs (citation needed). Finally, the structure of the Maven ecosystem,
gives us the oportunity to see if an artifact that is a dependency to a large
number of other artifacts contains a high rate of security bugs. In this case
we can strenghten the relationship between Linus' Law and software security as
Meneely et al. have already indicated~\cite{MW10}.

>>>>

The motivation behind our work is to validate if programmers tend to care for
such high-risk bugs when they release a new version of their software. In
addition, we want to investigate other critical aspects associated with such
vulnerabilities. For instance, we want to elaborate more on the relation of security
bugs not only with performance bugs (as Zaman et al.~\cite{ZAH11} have already
did) but also with other bug categories. In the same manner, we want to check
the relation between an artifact's size and its' security bugs knowing the
that research has been contradictory on the the issue~\cite{BP84, SYTP85,
NBZ06, GKMS00}.
Finally, the structure of the Maven ecosystem, gives us the oportunity to see
if an artifact that is a dependency to a large number of other artifacts
contains a high rate of security bugs. In this case
we can strenghten the relationship between Linus' Law and software security as
Meneely et al. have already indicated~\cite{MW10}.
